---
title: "Exploring China's Belt and Road Initiative Across Different Regions"
author: "Bethany Dickinson"
date: "9/24/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, error = FALSE)
```
source: <https://www.aiddata.org/data/chinese-global-official-finance-dataset>

```{r, include = TRUE, warning = FALSE, message = FALSE}

library(tidyverse)
BRI <- read_csv("GlobalChineseOfficialFinanceDataset_v1.0.csv")

```

# Visualization #1 - Africa
```{r Africa, warning = FALSE, message = FALSE}

Africa <- BRI %>%
  select(year, recipient_region, usd_current) %>%
  filter(recipient_region == "Africa") %>%
  arrange(year) %>%
  select(year, usd_current)

Africa_Avg <- Africa %>%
  group_by(year) %>%
  summarize(usd_current = mean(usd_current, na.rm =TRUE)) %>%
  mutate(usd_current_avg = usd_current/1000000) %>%
  round(digits = 2)

Africa_Avg %>%
  ggplot() +
  geom_point(aes(x = year, y = usd_current_avg), size = 0.5) +
  geom_smooth(aes(x = year, y = usd_current_avg)) +
  scale_x_continuous(breaks = seq(2000, 2014, by = 1)) +
  #scale_y_continuous(breaks = seq(30, 300, by = 50)) +
  theme(axis.text.x = element_text (face = "bold", size = 10, angle = 45))+
  labs(title = "Figure 1. Infrastructure Project Costs in Africa from 2000-2014",
       subtitle = "Chinese infrastructure investment across Africa",
       caption = "Source: AidData's Global Chinese Official Finance Dataset, 2000-2014, v.1.0",
       y = "Project Costs (million USD)",
       x ="Year") 
```


**Interpretation**: Figure 1. shows a general trend of increasing infrastructure costs on the African continent by the Chinese government. Each year shows the average cost of all projects in the region. The general trend has been a relatively steady increase until 2010, where the continent saw a huge spike in infrastructure investment. 



## Visualization #2 - Asia
```{r Asia, fig.width = 10, fig.asp = 0.8, warning = FALSE, message = FALSE}

Asia <- BRI %>%
  select(year, recipient_region, usd_current) %>%
  filter(recipient_region == "Asia") %>%
  arrange(year) %>%
  select(year, usd_current)

Asia_Avg <- Asia %>%
  group_by(year) %>%
  summarize(usd_current = mean(usd_current, na.rm =TRUE)) %>% 
  mutate(usd_current_avg = usd_current/1000000) %>%
  round(digits = 2)
  
ggplot(Asia_Avg, aes(year, usd_current_avg)) +
  geom_col(aes(fill = usd_current_avg, position = "dodge"), fill = "purple") +
  geom_text(aes(label = usd_current_avg), position = position_dodge(0.2)) +
  scale_x_continuous(breaks = seq(2000, 2014, by = 1)) +
  scale_y_continuous(breaks = seq(20, 500, by = 50)) +
  theme(axis.text.x = element_text (face = "bold", size = 10, angle = 45)) +
  labs(title = "Figure 2. Infrastructure Project Costs in Asia from 2000-2014",
       subtitle = "Chinese infrastructure investment across Asia",
       caption = "Source: AidData's Global Chinese Official Finance Dataset, 2000-2014, v.1.0",
       y = "Project Costs (million USD)",
       x ="Year") 

```


**Interpretation**: Figure 2. shows infrastructure investment by the Chinese government from 2000-2014. The pattern of investment has been inconsistent over the years. It does not show a general trend upwards like that of the African continent. Similar to the Africa region, investment saw its biggest costs in 2010. More research will need to be conducted in order to explain a possible relationship of why infrastructure spiked in 2010 for both regions. 





## Visualization #3 - The Middle East
```{r The Middle East, warning = FALSE, message = FALSE}

Middle_East <- BRI %>% 
  select(year, recipient_region, usd_current) %>%
  filter(recipient_region == "Middle East") %>%
  arrange(year) %>%
  select(year, usd_current)

The_MidEast_Avg <- Middle_East %>%
  group_by(year) %>%
  summarize(usd_current = mean(usd_current, na.rm =TRUE)) %>%
  mutate(usd_current2 = usd_current/1000000) 
  round(digits = 2)
  
The_MidEast_Avg %>%
  ggplot() +
  geom_line(aes(x = year, y = usd_current2), color = "red") +
  geom_point(aes(x = year, y = usd_current2, shape = "plus")) +
  scale_x_continuous(breaks = seq(2000, 2014, by = 1)) +
  #scale_y_continuous(breaks = seq(700, 77000, by = 7000)) +
  theme(axis.text.x = element_text (face = "bold", size = 10, angle = 45))+
  labs(title = "Figure 3. Infrastructure Project Costs in the Middle East from 2000-2014",
       subtitle = "Chinese infrastructure investment across the Middle East",
       caption = "Source: AidData's Global Chinese Official Finance Dataset, 2000-2014, v.1.0",
       y = "Project Costs (million USD)",
       x ="Year") 
```

**Interpretation**: Figure 3. shows the biggest annual increase in infrastructure investment compared to Asia and Africa. The Middle East saw an enormous surge in infrastructure projects in the last 6 or 7 years. This spike must been explored more to explain the exponential growth. Prior to 2013, infrastructure costs were relatively low for over a decade compared to other regions.





## Visualization #4 - The Pacific 

```{r The Pacific Region, warning = FALSE, message = FALSE}

The_Pacific <- BRI %>%
  select(year, recipient_region, usd_current) %>%
  filter(recipient_region == "The Pacific") %>%
  arrange(year) %>%
  select(year, usd_current) 

The_Pacific_Avg <- The_Pacific %>%
  group_by(year) %>%
  summarize(usd_current = mean(usd_current, na.rm =TRUE)) %>%
  mutate(usd_current2 = usd_current/100000) %>%
  round(digits = 2)

The_Pacific_Avg %>%
  ggplot() +
  geom_line(aes(x = year, y = usd_current2), color = "blue") +
  geom_point(aes(x = year, y = usd_current2), shape = "triangle") +
  scale_x_continuous(breaks = seq(2000, 2014, by = 1)) +
  #scale_y_continuous(breaks = seq(700, 77000, by = 7000)) +
  theme(axis.text.x = element_text (face = "bold", size = 10, angle = 45))+
  labs(title = "Figure 4. Infrastructure Project Costs in the Pacific from 2000-2014",
       subtitle = "Chinese infrastructure investment across the Pacific",
       caption = "Source: AidData's Global Chinese Official Finance Dataset, 2000-2014, v.1.0",
       y = "Project Costs (million USD)",
       x ="Year") 

```

**Interpretation**: Figure 4. shows a lot of variability in infrastructure investment in the Pacific region over 15 years. Unlike Asia and Africa, the Pacific did not see a spike in investment in 2010. Their biggest spikes occurred in 2002, 2007 and 2012; exactly five years apart for each period. 





## Visualization #5 - All Regions

``` {r all regions, fig.width = 10, fig.asp = 0.8,  warning = FALSE, message = FALSE }

BRI_regions <- BRI %>%
  select(recipient_region, usd_current, year) %>%
  arrange(recipient_region, year)
 
BRI_regions_avg <- BRI_regions %>%
  group_by(recipient_region, year) %>%
  summarize(usd_current = mean(usd_current, na.rm = TRUE)) %>%
  mutate(usd_current = usd_current/1000000)

BRI_regions_avg %>%
  ggplot() +
  geom_line(aes(x = year, y = usd_current, color = recipient_region), linetype = 7) +
  geom_point(aes(x = year, y = usd_current, shape = "diamond"), fill = "black")+
  scale_x_continuous(breaks = seq(2000, 2014, by =1)) +
  scale_y_continuous("usd_current") +
  theme(axis.text.x = element_text (face = "bold", size = 10, angle = 45))+
  labs(title = "Figure 5. Infrastructure Project Costs Across 6 Regions from 2000-2014",
       subtitle = "Chinese Infrastructure Investment",
       caption = "Source: AidData's Global Chinese Official Finance Dataset, 2000-2014, v.1.0",
       y = "Project Costs (million USD)",
       x ="Year") 
 
```

**Interpretation**: Figure 5. shows regional comparisons of infrastructure investment from 2000-2014. All regions except the Pacific have seen increasing activity and project costs over the past 15 years. Central and Eastern Europe saw the biggest spikes in investment in 2009 and 2012 compared to other regions. However in 2014, the Middle East saw the largest investment in costs compared to all regions over the the entire 15 year period. 






# Visualization #6 - All Regions
```{r, warning = FALSE, message = FALSE}

BRI_circle <- BRI %>%
  select(recipient_region, usd_current, year) %>%
  filter(year == "2014") %>%
  group_by(recipient_region, year) %>%
  summarize(usd_current = mean(usd_current, na.rm = TRUE)) %>%
  mutate(usd_current = usd_current/1000000)

  
BRI_circle %>%
  ggplot(aes(x = "", y = usd_current, fill = recipient_region)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar("y", start = 0) +
  labs(title = "Figure 6. Infrastructure Project Costs by Region in 2014",
       subtitle = "Average costs from 2014 across all regions",
       caption = "Source: AidData's Global Chinese Official Finance Dataset, 2000-2014, v.1.0",
       y = "Project Costs (million USD)",
       x ="Year") 

#note: this needs work and I should've converted these amounts to percentages, but ran out of time. I just wanted to see what this looked like. 
```
**Interpretation**: Figure 6. shows the breakdown of Chinese infrastructure investment in 2014 across all regions. The Middle East had the largest investment costs compared to all regions, at least 60%. This proportion is also evident in Figure 5. Central and Eastern Europe and Latin America and the Caribbean were the second and third highest investment regions. 